Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Preparing data for England and Greater London

>>>>

The following code is to compare mortality rates per one, by age groups of 5 and sex for England and England.

ALSO PART OF THE BELOW CODE WILL BE NEEDED FOR THE MSLT AND DISMOD COLLECTION. GENERATE DATA INPUTS FOR DISMOD II FROM HERE.

```{r, echo=TRUE}
#Data preparation (generate age groups, change capitals to lower case)
##All upper cases to lower cases

GBDdata <- mutate_all(GBDdata, funs(tolower))

##Create age categories index in GBDdata (rounding mid age)

GBDdata$age_cat [GBDdata$age =="under 5"] <- 2
GBDdata$age_cat [GBDdata$age =="5 to 9"] <- 7
GBDdata$age_cat [GBDdata$age =="10 to 14"] <- 12
GBDdata$age_cat [GBDdata$age =="15 to 19"] <- 17
GBDdata$age_cat [GBDdata$age =="20 to 24"] <- 22
GBDdata$age_cat [GBDdata$age =="25 to 29"] <- 27
GBDdata$age_cat [GBDdata$age =="30 to 34"] <- 32
GBDdata$age_cat [GBDdata$age =="35 to 39"] <- 37
GBDdata$age_cat [GBDdata$age =="40 to 44"] <- 42
GBDdata$age_cat [GBDdata$age =="45 to 49"] <- 47
GBDdata$age_cat [GBDdata$age =="50 to 54"] <- 52
GBDdata$age_cat [GBDdata$age =="55 to 59"] <- 57
GBDdata$age_cat [GBDdata$age =="60 to 64"] <- 62
GBDdata$age_cat [GBDdata$age =="65 to 69"] <- 67
GBDdata$age_cat [GBDdata$age =="70 to 74"] <- 72
GBDdata$age_cat [GBDdata$age =="75 to 79"] <- 77
GBDdata$age_cat [GBDdata$age =="80 to 84"] <- 82
GBDdata$age_cat [GBDdata$age =="85 to 89"] <- 87
GBDdata$age_cat [GBDdata$age =="90 to 94"] <- 92
GBDdata$age_cat [GBDdata$age =="95 plus"] <- 97

##Convert variable val to numberic

GBDdata$val <- as.numeric(as.character(GBDdata$val))

##Filter data for England and Greater London adn generate per person rates (per 100,000 in original data)
#England
GBDEngland <- filter(GBDdata, location == "england" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)

GBDEngland$one_rate <- GBDEngland$val/100000

#Greater London (GL)
GBDGL <- filter(GBDdata, location == "greater london" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)
GBDGL$one_rate <- GBDGL$val/100000

```
